Additional analysis

### 2018-04-08 03_additional-analysis.Rmd
Nicer misc tables

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(ggridges)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  pandoc.table()
```

@@

```{r attention-check-2, results="asis"}
results %>% count(attention2_correct) %>% pandoc.table()
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(ggridges)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  gather(Statistic, value) %>% 
  mutate(value = seconds_to_period(value)) %>% 
  mutate(Minutes = sprintf("%02d:%02d", minute(value), second(value))) %>% 
  select(-value) %>% 
  pandoc.table()
```

@@

```{r attention-check-2, results="asis"}
results %>% count(attention2_correct) %>% 
  rename(`Attention check 2 correct` = attention2_correct, Count = n) %>% 
  pandoc.table()
```
